### 2018-07-24 modelling.tex
Add Kruschke-like diagram and fix some section referencing

The Bayes theorem is an extremely versatile tool taking a role analogous to that of statistics like T, F, or $\chi^2$. Unlike them, which are tailored to specific scenarios, it can be used compute the probability distribution of almost any parameter in any model. 4 terms can be distinguished in its expression

@@

The Bayes\textquotesingle s theorem formulated above is thus read as \textit{the posterir probability of the parameter $\theta$ is equal to the \textbf{prior} probability distribution times the likelihood divided by a constant}.

@@

>>>>

The Bayes theorem is an extremely versatile tool taking a role analogous to that of statistics like T, F, or $\chi^2$. Unlike them, which are tailored to specific scenarios, it can be used to compute the probability distribution of almost any parameter in any model. 4 terms can be distinguished in its expression

@@

The Bayes\textquotesingle s theorem formulated above is thus read as \textit{the posterior probability of the parameter $\theta$ is equal to the \textbf{prior} probability distribution times the likelihood divided by a constant}.

@@

\begin{figure}[!h]
 \centering 
 \includepdf[pages=-]{hierarch_diagram.pdf}
\end{figure}

### 2018-07-24 pipeline.tex
Add Kruschke-like diagram and fix some section referencing

\begin{figure}[!h]
\includegraphics[width=0.8\textwidth]{match_percent}
\caption[Percentage of matched spectra in all samples]{The total number of spectra per sample ranged between 5894 and 20249. \textbf{A} Percentages are encoded with a blue palette, the darker, the higher, and viceversa. \textbf{B} The mean for each analysed fraction across conditions and replicates is displayed together with error bars to represent the standard deviation. The sixth fraction of the first replicate in condition H was missing in the PRIDE data repository.}
\label{fig:match_percent}
\end{figure}

>>>>

\begin{figure}[!h]
\centering
\includegraphics[width=0.8\textwidth]{match_percent}
\caption[Percentage of matched spectra in all samples]{\textbf{Percentage of matched spectra in all samples}. The total number of spectra per sample ranged between 5894 and 20249. \textbf{A} Percentages are encoded with a blue palette, the darker, the higher, and viceversa. \textbf{B} The mean for each analysed fraction across conditions and replicates is displayed together with error bars to represent the standard deviation. The sixth fraction of the first replicate in condition H was missing in the PRIDE data repository.}
\label{fig:match_percent}
\end{figure}

### 2018-07-24 thp1.tex
Add Kruschke-like diagram and fix some section referencing

The protein ratios across conditions are not known in ordinary datasets In order to judge the resolving power of the mass spectrometry and shotgun proteomics workflows presented in this work, an in-house dataset attempting to capture an immunological response was generated. Therefore, even though true protein ratios were not known \textit{a priori}, the analysis should find proteins related to the immunological response to be significantly differentially abundant.

@@

After preprocessing and missing-data handling, a dataset of 1641 peptides was input to BayesQuant, and 269 proteins were quantified. A histogram of the mean of the inferred posterior distributions manifests the centrality of its distribution, with most values within the predefined \ac{ROPE} of [-0.4, 0.4]. In line with what was observed in the results above, the distribution was found to be skewed toward negative values (see figure \ref{fig:compomics_bq}A). Only four proteins were assigned a 95\% \ac{HPDI} not touching the \ac{ROPE} (see figure \ref{fig:compomics_bq}B and table \ref{tab:thp1_bq_results}). The distribution of the \ac{HPDI} width summarises the overall uncertainty in the estimation process. Most proteins had a very narrow HPDI, as shown in figure \ref{fig:compomics_bq}C. As expected, the width of the interval exhibited some degree of correlation with   the mean of the posterior, as shown in \ref{fig:compomics_bq}D.

>>>>

The protein ratios across conditions are not known in ordinary datasets. In order to judge the resolving power of the mass spectrometry and shotgun proteomics workflows presented in this work, an in-house dataset attempting to capture an immunological response was generated. Therefore, even though true protein ratios were not known \textit{a priori}, the analysis should find proteins related to the immunological response to be significantly differentially abundant.

@@

After preprocessing and missing-data handling, a dataset of 1641 peptides was input to BayesQuant, and 269 proteins were quantified. A histogram of the mean of the inferred posterior distributions manifests the centrality of its distribution, with most values within the predefined \ac{ROPE} of [-0.4, 0.4]. In line with what was observed in the results above, the distribution was found to be skewed toward negative values (see figure \ref{fig:compomics_bq}A). Only four proteins were assigned a 95\% \ac{HPDI} not touching the \ac{ROPE} (see figure \ref{fig:compomics_bq}B and table \ref{tab:thp1_bq_results}). The distribution of the \ac{HPDI} width summarises the overall uncertainty in the estimation process. Most proteins had a very narrow HPDI, as shown in figure \ref{fig:compomics_bq}C. As expected, the width of the interval exhibited some degree of correlation with the mean of the posterior, as shown in figure \ref{fig:compomics_bq}D.
